Title of submission to PLOS journal

### 2019-08-26 docs/manuscript_draft.Rmd
remove dendrogram labels

### overall patterns of sample similarity

@@

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
source("../analysis/08_WGCNA_1.R")
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")

@@

## subset by sex and tissue

>>>>

@@

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
source("../analysis/08_WGCNA_1.R")
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram of samples")
```

@@
